Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-10 be.tex
spell checker

The critical heating value $\zeta_c$ is an increasing function of
$r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp
galaxies, since a greater heating rate is required to unbind gas from
a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).  Specifically,
we find $\zeta_c\sim (\rb/\rinf)^{0.5(1-\Gamma)}$ for $\rb\gsim\rinf$
(see the top panel of Fig.~\ref{fig:zetaCrit} for the case of core
galaxies). Likewise the minimum $r_{\rm s,min}/r_{b}$ is an increasing
function of $\zeta/\zeta_{c}$, approaching unity for $\zeta <
0.86\zeta_c$, as shown in the bottom panel of Fig.~\ref{fig:zetaCrit}.
As $\zeta \rightarrow 0.86\zeta_c$ our numerical simulations show that
that the stagnation radius diverges from its value predicted by
equations (\ref{eq:stag_analytic}) and (\ref{eq:densSlope}) and moves
out to the break radius.

>>>>

The critical heating value $\zeta_c$ is an increasing function of
$r_{b}/r_{\rm inf}$ and is larger for core galaxies than cusp
galaxies, since a greater heating rate is required to unbind gas from
a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).  Specifically,
we find $\zeta_c\sim (\rb/\rinf)^{0.5(1-\Gamma)}$ for $\rb\gsim\rinf$
(see the top panel of Fig.~\ref{fig:zetaCrit} for the case of core
galaxies). Likewise the minimum $r_{\rm s,min}/r_{b}$ is an increasing
function of $\zeta/\zeta_{c}$, approaching unity for $\zeta <
0.86\zeta_c$, as shown in the bottom panel of Fig.~\ref{fig:zetaCrit}.
As $\zeta \rightarrow 0.86\zeta_c$ our numerical simulations show that
that the stagnation radius diverges from its value predicted by
equations (\ref{eq:stag_analytic}) and (\ref{eq:densSlope}) and moves
out to the break radius.

### 2015-04-10 windheat.tex
spell checker

In the case of a single implusive burst of star formation, the mass
and energy injection rate per unit stellar mass at time $t$ after the
burst are given, respectively, by
\begin{align} 
  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu|_{M_{\rm TO}(t)}
    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
        T}(t)}
    \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar }{\bar{m}_*}\\
  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}(t)+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
  \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
  \label{eq:edotImp}
\end{align} 
where the first and second terms in each expression corresponds to
contributions from main sequence (MS) stars and post-main sequence
(PMS) stars, respectively.  Here $ f_{\rm MS} < 1$ is the efficiency
with which main sequence winds thermalize their energy with the rest
of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$
is the IMF, which we take to be of the Salpeter form $\mu|_{\Mstar}
\propto M_{\star}^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low
mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ =
0.35 $\Msun$ is the corresponding mean stellar mass.  Our optimistic
assumption of 100 per cent thermalization efficiency of stellar winds
is at least partially offset by our conservative assumption to neglect
energy input from core collapse supernovae, which contribute a
comparable energy injection rate to massive stellar winds.

@@

 \begin{figure}
  \includegraphics[width=\columnwidth]{bumpy.pdf}
  \caption{\label{fig:NickPlot2} Effective wind velocities for
    nonstandard star formation histories.  The black curves shows, for
    reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$,
    and gray curves show wind heating resulting from perturbed star
    formation histories given by equation~\eqref{eq:sfrPerturbed}. In
    the top panel the star formation rate declines for a time, $\delta
    t_*=10^{7}$ years to fractions $\iota= 0.001$ (dashed), $\iota
    =0.1$ (dotted), and $\iota = 0.3$ (dot-dashed) of the halo
    averaged value. The bottom panel shows results for $\delta
    t_*=10^{8}$ years and $\iota$=0.001 (dashed) and 0.1 (dotted).}
  \end{figure}
  We estimate the stellar wind heating provided by the {\it average}
  star formation history of galaxies of a given $\Mbh$ using the
  results of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
  star formation histories in \citet{MosterNaab+:2013a} are in terms
  of halo mass. For a given $\Mbh$ we assign the halo mass whose star
  formation history would produce a bulge consistent with the
  $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A
  slight complication occurs for the largest mass halos, where much of
  the $z=0$ stellar mass has been acquired through accretion of
  satellite halos rather than {\it in situ} star formation.  To
  accomodate this, we incorporate analytic fits for mass accretion
  histories, taken from \citet[their eqs.~21-23]{MosterNaab+:2013a},
  assuming that the age distribution of the accreted stars is equal to
  the age distribution of those formed {\it in situ}.  This assumption
  may be conservative if the primary galaxy's accretion history is
  dominated by minor mergers with younger stellar populations.  On the
  other hand, the dynamical friction inspiral time for small satellite
  galaxies is quite long, generally much greater than the $\sim
  10^7~{\rm yr}$ for which young stars can dominate the heating
  budget.  The mass of stars accreted for halo masses, $M_{\rm halo}< 3
  \times 10^{12} \Msun$, and redshifts, $z>4$, is small and is neglected.

>>>>

In the case of a single impulsive burst of star formation, the mass
and energy injection rate per unit stellar mass at time $t$ after the
burst are given, respectively, by
\begin{align} 
  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu|_{M_{\rm TO}(t)}
    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
        T}(t)}
    \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar }{\bar{m}_*}\\
  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}(t)+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
  \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
  \label{eq:edotImp}
\end{align} 
where the first and second terms in each expression corresponds to
contributions from main sequence (MS) stars and post-main sequence
(PMS) stars, respectively.  Here $ f_{\rm MS} < 1$ is the efficiency
with which main sequence winds thermalize their energy with the rest
of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$
is the IMF, which we take to be of the Salpeter form $\mu|_{\Mstar}
\propto M_{\star}^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low
mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ =
0.35 $\Msun$ is the corresponding mean stellar mass.  Our optimistic
assumption of 100 per cent thermalization efficiency of stellar winds
is at least partially offset by our conservative assumption to neglect
energy input from core collapse supernovae, which contribute a
comparable energy injection rate to massive stellar winds.

@@

 \begin{figure}
  \includegraphics[width=\columnwidth]{bumpy.pdf}
  \caption{\label{fig:NickPlot2} Effective wind velocities for
    nonstandard star formation histories.  The black curves shows, for
    reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$,
    and gray curves show wind heating resulting from perturbed star
    formation histories given by equation~\eqref{eq:sfrPerturbed}. In
    the top panel the star formation rate declines for a time, $\delta
    t_*=10^{7}$ years to fractions $\iota= 0.001$ (dashed), $\iota
    =0.1$ (dotted), and $\iota = 0.3$ (dot-dashed) of the halo
    averaged value. The bottom panel shows results for $\delta
    t_*=10^{8}$ years and $\iota$=0.001 (dashed) and 0.1 (dotted).}
  \end{figure}
  We estimate the stellar wind heating provided by the {\it average}
  star formation history of galaxies of a given $\Mbh$ using the
  results of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
  star formation histories in \citet{MosterNaab+:2013a} are in terms
  of halo mass. For a given $\Mbh$ we assign the halo mass whose star
  formation history would produce a bulge consistent with the
  $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A
  slight complication occurs for the largest mass halos, where much of
  the $z=0$ stellar mass has been acquired through accretion of
  satellite halos rather than {\it in situ} star formation.  To
  accommodate this, we incorporate analytic fits for mass accretion
  histories, taken from \citet[their eqs.~21-23]{MosterNaab+:2013a},
  assuming that the age distribution of the accreted stars is equal to
  the age distribution of those formed {\it in situ}.  This assumption
  may be conservative if the primary galaxy's accretion history is
  dominated by minor mergers with younger stellar populations.  On the
  other hand, the dynamical friction inspiral time for small satellite
  galaxies is quite long, generally much greater than the $\sim
  10^7~{\rm yr}$ for which young stars can dominate the heating
  budget.  The mass of stars accreted for halo masses, $M_{\rm halo}< 3
  \times 10^{12} \Msun$, and redshifts, $z>4$, is small and is neglected.
